Near Optimal Behavior with Approximate State Abstraction

### 2016-02-03 paper/conclusion.tex

% Future work.
There are many directions for future work. First, we are interested investigating learning approximate abstraction functions online in the planning or learning setting, first proposed by \citeauthor{ortner2013adaptive} who learned the approximate criteria of $\epsilon$-homogeneity with UCRL~\cite{ortner2007logarithmic}. Learning abstraction functions online also has interesting implications for the exploration problem. If certain information can inform the agent's ability to abstract more quickly, then exploration directed at learning the abstraction function introduces a new notion of exploration, since an abstraction function will enable the agent to identify near-optimal behavior more quickly,

We are also interested in approximate relaxations of additional classes of abstraction functions, and in characterizing the necessary conditions for an abstraction that will preserve any notion of optimality. In particular, the abstraction class $\phi_{a^*}$ discussed by~\cite{li2006towards}, which is guaranteed to collapse states that share the optimal action and the optimal actions $Q^*$ value. To do this properly, one must apply confidence intervals to the event of each action's optimality, in addition to relaxing $Q^*$ equivalence to similarity. This abstraction class may also introduce compelling connections to temporal abstractions, including Options, discussed at length in reinforcement learning and planning \dnote{Options citations}. We investigated the use of options in the Taxi domain under $\phi_{a^*}$, and found a negligible difference in the degree and quality of compression compared to the compression without Options. In future work, we are interested in characterizing the relationship between temporal abstractions and approximate abstraction. Lastly, we are investigating the relationship between various approximate abstractions and the information theoretical limitations on the compressibility of certain classes of \acp{MDP}.

>>>>

% Future work.
There are many directions for future work.

% Learning abs functions online.
First, we are interested investigating learning approximate abstraction functions online in the planning or learning setting, first proposed by \citeauthor{ortner2013adaptive} who learned the approximate criteria of $\epsilon$-homogeneity with UCRL~\cite{ortner2007logarithmic}.

% Exploration is interesting.
Learning abstraction functions online also has interesting implications for the exploration problem. If certain information can inform the agent's ability to abstract more quickly, then exploration directed at learning the abstraction function introduces a new notion of exploration, since an abstraction function will enable the agent to identify near-optimal behavior more quickly,

% Necessary conditions.
One question of interest is what the necessary conditions are for an abstraction that will preserve any notion of optimality (i.e. the bound between the values under $\pi_G^*$, $\pi_{G,A}$ is less than $\textsc{VMax}$). In future work, we are interested in identifying these conditions.

% Options/termporal abstraction
In future work, we are interested in characterizing the relationship between temporal abstractions, such as those afforded by Options, and approximate abstractions. Options have been discussed at length in reinforcement learning and planning \dnote{Options citations}. We investigated the use of options in the Taxi domain, and found a negligible difference in the degree and quality of compression compared to compression without Options.

% Compressibility
Lastly, we are investigating the relationship between various approximate abstractions and the information theoretical limitations on the compressibility of certain classes of \acp{MDP}.
